Template for GTEx example on cluster

### 2017-10-01 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

#SBATCH --job-name=arrayJob
#SBATCH --output=/home/weidong/HG/flash/data/GTEX/testflashr2/outlog/arrayJob_%A_%a.out
#SBATCH --error=/home/weidong/HG/flash/data/GTEX/testflashr2/outlog/arrayJob_%A_%a.err
#SBATCH --array=1
#SBATCH --time=32:00:00
#SBATCH --partition=mstephens
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --mem-per-cpu=20G

>>>>

#SBATCH --job-name=arrayJob
#SBATCH --output=/home/weidong/HG/flash/data/GTEX/testflashr2/outlog/arrayJob_%A_%a.out
#SBATCH --error=/home/weidong/HG/flash/data/GTEX/testflashr2/outlog/arrayJob_%A_%a.err
#SBATCH --array=1
#SBATCH --time=30:00:00
#SBATCH --partition=mstephens
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --mem-per-cpu=8G
